---
title: "conda_notes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{conda_notes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hempTools)
```



The 'conda' environment, and it's variants such as anaconda and miniconda, allows the user to spawn an environment that allows them to make version specific installations of software.
Because this occurs in an 'environment' instead of on the main system, it allows for this system to be deployed on shared computing systems.
This document contains notes on the use of these environments.


## Links


[conda user's guide](https://docs.conda.io/projects/conda/en/latest/user-guide/index.html)    

[CQLS conda tutorial](https://software.cqls.oregonstate.edu/tips/posts/conda-tutorial/)    


## A conda session


The conda system does not appear to work well with csh/tcsh, so we use bash.
This can be accomplished by typing `bash` at the command prompt.
One way to determine if conda is already installed is to quesry it's version.


```
bash
conda --version
```


If this reports a version, then conda must be installed.
If it does not report a version but reports an error, then you probably need to install conda.

Another way to determine if conda is installed, and to determine which environments exist, is to query the environments.

```
(base) knausb@trifolium:~$ conda info --envs
# conda environments:
#
                         /home/knausb/.local/share/r-miniconda
                         /home/knausb/.local/share/r-miniconda/envs/r-reticulate
base                  *  /home/knausb/miniconda3
biopython                /home/knausb/miniconda3/envs/biopython
clang                    /home/knausb/miniconda3/envs/clang
```


The asterisk indicates which environment is active.
These results also report the location where the environment is installed.


If you'd like to activate an environment 

```
(base) knausb@trifolium:~$ conda activate biopython
(biopython) knausb@trifolium:~$ 
```

Note that the prompt has changed on my system, but this may be system specific.


If you wish to exit from conda you can deactivate it.


```
(biopython) knausb@trifolium:~$ conda deactivate
(base) knausb@trifolium:~$ conda deactivate
knausb@trifolium:~$ 
```


Note that the first `deactivate` command backed out of the `biopython` environment and retunred us to the `base` environment.
The second `deactivate` command exited from conda.
This can be seen in the prompt.


## Creating environments


A main reason for using `conda` is to use `environments` that have different software, and perhaps different versions of software, in them.



```
conda create --name snowflakes biopython
```








```
(base) bash-4.2$
```


```
bash-4.2$
```




To update conda use the following.


```
conda update conda
```


To see a list of all your environments, type:

```
conda info --envs
```


To create an environment named 'snowflakes' and installs biopython, use the following.


```
conda create --name snowflakes biopython
```


To use, or "activate" the new environment, type the following


```
conda activate snowflakes
```


Create an environment named 'snakes' that uses python 3.9.


```
conda create --name snakes python=3.9
```





