---
title: "conda_notes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{conda_notes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hempTools)
```



The 'conda' environment, and it's variants such as anaconda and miniconda, allows the user to spawn an environment that allows them to make version specific installations of software.
Because this occurs in an 'environment' instead of on the main system, it allows for this system to be deployed on shared computing systems.
This document contains notes on the use of these environments.


## Links


[conda user's guide](https://docs.conda.io/projects/conda/en/latest/user-guide/index.html)    

[CQLS conda tutorial](https://software.cqls.oregonstate.edu/tips/posts/conda-tutorial/)    


## A conda session


The conda system does not appear to work well with csh/tcsh, so on our HPC we use bash.


```
bash
conda --version
```


To update conda use the following.


```
conda update conda
```


To see a list of all your environments, type:

```
conda info --envs
```


To create an environment named 'snowflakes' and installs biopython, use the following.


```
conda create --name snowflakes biopython
```


To use, or "activate" the new environment, type the following


```
conda activate snowflakes
```


Create an environment named 'snakes' that uses python 3.9.


```
conda create --name snakes python=3.9
```





